Using Distributed Information Stores for Patient-Clinician Health Data Sharing

### 2013-01-15 patient-clinician-workshop/pccworkshop.tex
More about electronic sensors

>>>>

Currently these products tend to work in isolation, where the readings from a single product
are presented either on the device themselves, or via a smartphone or website. However,
their use could be integrated with clinical care, in order to monitor patients, and to give an
insight into their lifestyle.
